\ifx\master\undefined\input{settings/autocompile}\fi

\chapter{Analysis Selections}
\label{ch:selections}

\section{Particle Identification}
\subsection{Muons}
\label{sec:MuonId}

Muon candidates are required to be reconstructed as global and as tracker muons,
meaning that a full track is reconstructed in the muon system and is well
matched to a track in the silicon strip and pixel trackers.
Additionally, they are required to pass the ``Vector Boson Task Force'' (VBTF)
muon identification criteria developed for the $Z \to \mu^{+} \mu^{-}$
cross--section measurement~\cite{CMS-PAS-EWK-10-002}:
\begin{itemize}
\item $\geq 1$ Pixel hits
\item $\geq 10$ hits in silicon Pixel $+$ Strip detectors
\item $\geq 1$ hit(s) in muon system
\item $\geq 2$ matched segments
\item $\chi^{2}/DoF < 10$ for global track fit
\item transverse impact parameter of ``inner'' track $d_\text{IP} < 2~\milli\meter$
  with respect to beam--spot
\end{itemize}

In order to reduce background contributions from muons originating from heavy
quark decays in QCD multi--jet events, muons are required to be isolated.
Isolation is computed as the \pt sum of charged and neutral hadrons plus photons
reconstructed by the CMS particle--flow algorithm~\cite{CMS-PAS-PFT-09-001} within a
cone of size $\Delta R_{iso} = 0.4$ around the muon direction.  The innermost
region of size $\Delta R_{veto} = 0.08$ ($0.05$) is excluded from the
computation of the isolation \pt sum with respect to neutral hadrons (photons),
in order to avoid energy deposits in the electromagnetic and hadronic
calorimeters which are due to the muon to enter the sum.  In order to reduce
pile--up effects, particles entering the isolation \pt sum are required to have
transverse momenta $\pt > 1.0$~\GeVc.  Charged particles are additionally
required to originate from the same vertex as the muon.  The muons are required
to be isolated with respect to charged hadrons of $\pt > 1.0~\GeVc$ and photons
of $\pt > 1.5~\GeVc$ as reconstructed by the particle--flow
algorithm~\cite{CMS-PAS-PFT-09-001} in a cone of size $\Delta R = 0.4$ around
the direction of the muon.

\subsection{Hadronic Taus}

Hadronic decays of taus are identified by the \hpsTanc hybrid algorithm
described in Section~\ref{sec:TauId}.  The ``medium'' working point is used,
corresponding to an expected QCD fake--rate of about 1\%. $Z \to \MM$ background
contributions are largely due to muons which failed to get reconstructed as
global muons (thus failing the muon identification requirement) and are
misidentified as tau--jet candidates.  These muons are typically isolated and
have a large chance to pass the hadronic tau ID discriminators.  To reject these
events, hadronic taus are additionally required to pass an anti--muon veto
described in Section~\ref{sec:LightLeptonRejection}. 

\subsection{Missing Transverse Energy}

The missing transverse energy \MET, in the event is reconstructed based on the
vectorial momentum sum of particle candidates reconstructed by the
particle--flow algorithm~\cite{CMS-PAS-PFT-09-001, CMS-PAS-JME-10-005}.  In the
ideal case, the \MET corresponds to the vector sum of the transverse components
of all neutrinos in the event.  The \MET resolution in simulated $Z\to\MM$
events is found to be smaller (better) than in the data.   The reconstructed
\MET in the simulated events is ``smeared'' by a correction factor such that the
data and simulation are in agreement.  The ``Z--recoil'' \MET correction
procedure is described in Section~\ref{sec:ZRecoilCorr}.

% End particle ID section
\section{Event Selections}
The selections applied to the analysis are designed to reject large fractions of
the background while maintaining a high efficiency for identifying signal
(Higgs) events.  The backgrounds can be divided into two classifications:
``fake'' backgrounds, in which there is at least one misidentified hadronic tau
decay, and the irreducible $Z\to\TT$ background, which cannot\footnote{Due to
the differences in spin between the $Z$ (spin~1) and the Higgs (spin~0), it
maybe be possible to separate the two using spin correlations of the two tau
decays.} be distinguished from the potential presence of a Higgs boson of the
same mass.  Strategies for dealing with the irreducible $Z$ background will be
discussed in the Chapter~\ref{ch:results}.
The different fake backgrounds, their cross section, and the basic 
removal strategies are outlined in Table~\ref{tab:FakeBackgrounds}.
\begin{table}[t]
\begin{center}
\begin{tabular}{|l|c|}
\hline
Background & Cross Section (\pb) \\
QCD Heavy Flavor &  84679\footnote{The QCD cross section given here is after a
requirement that at least one muon with $\pt > 15~\GeVc$ is produced in the
event.} \\
$W \to \mu \nu + \text{jets}$ & 10435 \\
$Z \to \mu \mu + \text{jets}$ & 1666  \\
$\ttbar + \text{jets}$ & 158 \\
\hline
\end{tabular}
\end{center}
\begin{center}
\caption[Analysis backgrounds that include fake taus]{The different backgrounds
to the analysis presented in this thesis that include misidentified hadronic
taus.} \label{tab:FakeBackgrounds}
\end{center}
\end{table}

Events in the muon plus tau--jet channel are selected by requiring a muon of
$\pt^{\mu} > 15$~\GeVc within $ \left| \eta_{\mu} \right| < 2.1$ and a tau-jet
candidate of $\pt^{\tau\mbox{--jet}} > 20$~\GeVc within $ \left|
\eta_{\tau\mbox{--jet}} \right| < 2.3$.  The $\eta$ requirement on the muon
ensures that it is within the fiducial region of the muon trigger system.  The
$\eta$ requirement on the hadronic tau ensures it is well within the fiducial
region of the tracker ($|\eta| < 2.5$) and minimizes exposure to large QCD
backgrounds in the very forward region.

The muon and tau--jet candidate are required to be of opposite charge, as the
Higgs is neutral and charge is conserved.  The muon is required to be pass the
identification criteria described in Section~\ref{sec:MuonId}.   The tau-jet
candidate is required to pass the ``medium'' TaNC tau identification \fixme{is
it really medium??}
discriminator. 

Additional event selection criteria are applied to reduce contributions of
specific background processes. In order to reject this background, a dedicated
discriminator against muons is applied~\cite{CMS-PAS-PFT-08-001}. Remaining muon
background is suppressed by rejecting events which have a track of $\pt >
15~\GeV$ and for which the sum of energy deposits in ECAL plus HCAL is below
$0.25 \cdot P$ within a cylinder of of radius $15$~\centi\meter (ECAL) and
$25$~\centi\meter (HCAL), respectively.  The $\ttbar$ and \WpJets backgrounds
are suppressed by cuts on the transverse mass of the $\mu--\MET$ system and the
\Pzeta variable.  Contamination from $Z \to \TT$ events in which the
reconstructed tau--jet candidate is due to a $\tau \to e \nu \nu$ decay is
reduced by applying a dedicated tau ID discriminator against electrons.



The complete set of event selection criteria applied in the muon +
tau--jet channel are summarized in table~\ref{tab:AHtoMuTauEventSelection}.

\begin{table}[t]
\begin{center}

\begin{tabular}{|l|c|}
\hline
\multicolumn{2}{|c|}{Requirement} \\
\hline
\multirow{2}{12mm}{Trigger} & HLT\_Mu9 for MC \\
                            & {\it cf.}\ table~\ref{tab:AHtoMuTauTriggers} for Data \\ 
\hline
\multirow{2}{17mm}{Vertex}  & reconstructed with beam--spot constraint: \\
                           & $-24 < z_{vtx} < +24$~cm, $\left| \rho \right| <
                           2~\centi\meter$, $N_\text{DOF} > 4$ \\ 
\hline
\multirow{4}{10mm}{Muon}    & reconstructed as global Muon with: \\
                            & $\pt > 15~\GeV$, $\vert \eta \vert < 2.1$, VBTF
                            Muon ID passed, \\
                            & isolated within $\Delta R =0.4$ cone with respect to charged hadrons \\
                            & of $\pt > 1.0$~\GeV and neutral electromagnetic
                            objects of $\pt > 1.5$~\GeV \\ 
\hline
\multirow{4}{23mm}{Tau--jet Candidate} & reconstructed by HPS + TaNC combined Tau ID algorithm \\
                            & TaNC ``medium'' Tau ID discriminator \\
                            & and discriminators against electrons and muons passed, \\
                            & calorimeter muon rejection passed \\
\hline
\multirow{2}{23mm}{Muon + Tau--jet} & charge(Muon) + charge(Tau--jet) = 0, \\
                            & $\Delta R$(Muon, Tau--jet)$ > 0.5$ \\
\hline
\multirow{2}{20mm}{Kinematics} & $M_{T}$(Muon-MET)$ < 40$~\GeV \\
                            & $P_{\zeta} - 1.5 \cdot P_{\zeta}^{vis} > -20$~\GeV \\
\hline
\end{tabular}
\end{center}
\begin{center}
\caption{\captiontext Event selection criteria applied in the muon + tau--jet channel.}
\label{tab:AHtoMuTauEventSelection}
\end{center}
\end{table}

The events are triggered by a combination of muon and muon + tau--jet
``cross--channel'' triggers. For the muon triggers, paths with lowest $P_{T}$
thresholds are used as long as the path remained unprescaled (see
Table~\ref{tab:AHtoMuTauTriggers}). 
The muon + tau--jet ``cross--channel'' trigger paths increase the trigger efficiency for
events containing muons of transverse momenta close to the
$\pt^{\mu} > 15$~\GeVc cut threshold.
The trigger efficiency is measured in data via the tag--and--probe
technique. Details of the muon trigger efficiency measurement are
given in Section~\ref{sec:ZmumuTagAndProbe} of the appendix.
Monte Carlo simulated events are required to pass the
HLT\_Mu9 trigger path. Weights are applied to simulated events to account for the
difference between the simulated HLT\_Mu9 efficiency and the combined
efficiency of the set HLT\_Mu9, HLT\_IsoMu9, HLT\_Mu11, HLT\_IsoMu13,
HLT\_Mu15, HLT\_IsoMu9\_PFTau15 and HLT\_Mu11\_PFTau15 used to trigger
the data.

\begin{table}[t]
\begin{center}

\begin{tabular}{|l|c|}
\hline
Trigger path & run--range \\
\hline
HLT\_Mu9             & 132440 - 147116 \\
HLT\_IsoMu9          & 147196 - 148058 \\
HLT\_Mu11            & 147196 - 148058 \\
HLT\_Mu15            & 147196 - 149442 \\
HLT\_IsoMu13         & 148822 - 149182 \\
HLT\_IsoMu9\_PFTau15 & 148822 - 149182 \\
HLT\_Mu11\_PFTau15   & 148822 - 149182 \\
\hline
\end{tabular}
\end{center}
\begin{center}
\caption[High Level Trigger paths used to select $\mu + \tau_h$ events]{\captiontext
Muon and muon + tau--jet ``cross--channel'' trigger paths utilized to trigger
events in the muon + tau--jet channel in different data--taking periods.}
\label{tab:AHtoMuTauTriggers}
\end{center}
\end{table}

\ifx\master\undefined\input{settings/autocompile}\fi
