\ifx\master\undefined\input{settings/autocompile}\fi

\prelimheaders

\chapter*{Acknowledgments}

The completion of this thesis would have been possible without the 
support of my family, friends, and colleagues.

Over the past five years, I have had the great fortune of collaborating with my
advisor Professor John Conway and colleague Dr. Christian Veelken on the work
described in this thesis.  John has been an unflappable source of support,
encouragement, and wisdom, and has provided me with amazing opportunities.  John
has always inspired me to push the envelope beyond what I thought was possible,
which is the most fun way to do science.  Christian is one of the most gifted and
intellectually generous people I have ever met.  His infinite patience, love of
science, technical ability, and guidance have all shaped me to be a
better scientist.  I would also like to thank Dr. Simone Gennai for his
friendship and support, and for hosting me in Italy, where some of the work
described in Chapter~\ref{ch:tanc} was performed.

My wife Kristen has made me a happy person.  Kristen has provided a balance to
my life that has made me a better scientist and a better person.  She is also
the coolest person I know.  I am forever indebted to my parents, who have always
supported me to be whatever I want to be, encouraged my curiosity, and
surrounded me with interesting things and people.  Finally, I would like to
acknowledge the support of my pseudosiblings Greg Hinkle, Joel McWilliams,
Spencer Nance, Ryan Bellshaw, Dr. Kevin Early, and Dr. Jamison Galloway.
Jamison deserves special mention for many helpful discussions regarding
theoretical particle physics.

\ifx\master\undefined\input{settings/autocompile}\fi
