\ifx\master\undefined\input{../settings/autocompile}\fi

\prelimheaders

\chapter*{Acknowledgments}

\begin{quote}
\centering
There are, of course, too many people to thank. If you are reading this, thank \emph{you}.

Thank you, Jim, for sharing with me a whole new field of research, for reminding me to think about the \emph{big ideas}, for demonstrating that physicists can also go to Burning Man, and for incredible freedom in my research.

Thank you, Chris, for your fresh and surprising perspective, your keen eye for fonts, and the endless hours spent helping me compile bleeding matplotlib versions.

Thank you, Sean, for reminding me that sound is important, for introducing me to Mexican Coke, and for giving me an `in' with the new overlords.

Thank you, Benny, for teaching me about everything from assembly to soldering, for helping me keep my diodes straight, and for spending those many hours on bicycle experiments.

Thank you, Ami, for deep thoughts about deep space, and chocolate cake.

Thank you, Mark, for the canonical and grand canonical ensembles.

Thank you, Marcus, for not teaching me LQG and Farsi at the same time.

Thank you to my one and only and highly singular family. Mom and Dad, I may be one in $2^{23}$, but together you are two in $2^{46}$, which is a lot more than twice as amazing. Max and Molly, thanks for letting me be the oldest, so that we could all be in grad school together.

Thank you, Diane and Keith, for being curious about what I do.

Thank you to Chance, for here we are on a hot planet in a cold Universe and things are so very interesting.

And thank you, Nora, te juro que no vivo un d\'{i}a m\'{a}s sin ti..
\end{quote}


\ifx\master\undefined\input{../settings/autocompile}\fi
